Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-05 paper.tex
Minor formatting update on table widths
Removed numbers from abstract

\begin{abstract}
This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing distortions commonly seen in real-world document image datasets.
Augraphy stands apart from other data augmentation tools by providing many different strategies to produce augmented versions of clean document images that appear as if they have been altered by standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for (1) producing diverse training data for tasks such as document de-noising, and (2) generating challenging test data for evaluating model robustness on document image modeling tasks.

@@

Many machine learning operations involving documents are impacted by the presence of noise, while high-level tasks like document classification and information extraction are frequently expected to perform well even on noisily-scanned document images.
For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
The lower-level task of document de-noising tackles the document noise problem directly, by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
All of these tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.

\begin{figure}
    \centering\scalebox{0.475}{
    \includegraphics{figures/archetype-memo.pdf}}
    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the noise seen in (a), which is a real-life sample from  RVL-CDIP. We re-created a clean version of (a) in (b). We then create a noisy version of (b) by applying several augmentations to it to produce (c).}
    \label{fig:intro}
\end{figure}

@@

\begin{table}[]
    \centering
    \caption{Comparison of various image-based data augmentation libraries. Number of augmentations is a rough count, and many augmentations in other tools are what Augraphy calls Utilities. Further, many single augmentations in Augraphy --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
    \scalebox{0.9}{
    \begin{tabular}{lccccc}
    \toprule
        \textbf{Library} & \textbf{Num.} & \textbf{Document-} & \textbf{Pipeline-} & & \\
        \textbf{Name} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
    \midrule
        \emph{Augmentor} \cite{augmentor} & 27 & \xmark &  & \cmark & MIT \\
        \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
        \emph{imgaug} \cite{ref_imgaug} & 168 & \xmark & \cmark & \cmark & MIT \\
        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & & \cmark & MIT \\
        \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
        \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
    \bottomrule
    \end{tabular}}
    \label{tab:augmentation-library-comparison}
\end{table}

@@

\begin{table}[]
    \centering
    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase, in suggested position within the pipeline. Augmentations that work well in more than one phase are listed in the last column.}
    \scalebox{0.81}{
    \begin{tabular}{llll}
    \toprule
        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} & \textbf{Multiple} \\
        \midrule
        \textsf{BleedThrough} &  \textsf{ColorPaper}& \textsf{BadPhotoCopy} & \textsf{BrightnessTexturize} \\
        \textsf{LowInkLines} & \textsf{Watermark} & \textsf{BindingsAndFasteners} & \textsf{DirtyDrum} \\
        \textsf{InkBleed} & \textsf{Gamma} & \textsf{BookBinding} & \textsf{DirtyRollers} \\
        \textsf{Letterpress} & \textsf{LightingGradient} & \textsf{Folding} & \textsf{Dithering} \\
        & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
        & & \textsf{Markup} & \textsf{NoiseTexturize}\\
        & & \textsf{Faxify} & \textsf{PencilScribbles}\\
        & & \textsf{PageBorder} & \\
        \bottomrule
    \end{tabular}}
    \label{tab:augmentations}
\end{table}

>>>>

\begin{abstract}
This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing distortions commonly seen in real-world document image datasets.
Augraphy stands apart from other data augmentation tools by providing many different strategies to produce augmented versions of clean document images that appear as if they have been altered by standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for producing diverse training data for tasks such as document denoising, and generating challenging test data for evaluating model robustness on document image modeling tasks.

@@

Many machine learning operations involving documents are impacted by the presence of noise, while high-level tasks like document classification and information extraction are frequently expected to perform well even on noisily-scanned document images.
For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
The lower-level task of document denoising tackles the document noise problem directly, by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
All of these tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.

\begin{figure}
    \centering

    \resizebox{\textwidth}{!}{
    \includegraphics{figures/archetype-memo.pdf}}

    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the noise seen in (a), which is a real-life sample from  RVL-CDIP. We re-created a clean version of (a) in (b). We then create a noisy version of (b) by applying several augmentations to it to produce (c).}

    \label{fig:intro}
\end{figure}

@@

\begin{table}[]
    \centering
    \caption{Comparison of various image-based data augmentation libraries. Number of augmentations is a rough count, and many augmentations in other tools are what Augraphy calls Utilities. Further, many single augmentations in Augraphy --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
    \resizebox{0.9\textwidth}{!}{
    \begin{tabular}{lccccc}
    \toprule
         & \textbf{Number of} & \textbf{Document} & \textbf{Pipeline} & & \\
        \textbf{Library} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
    \midrule
        \emph{Augmentor} \cite{augmentor} & 27 & \xmark &  & \cmark & MIT \\
        \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
        \emph{imgaug} \cite{ref_imgaug} & 168 & \xmark & \cmark & \cmark & MIT \\
        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & & \cmark & MIT \\
        \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
        \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
    \bottomrule
    \end{tabular}}
    \label{tab:augmentation-library-comparison}
\end{table}

@@

\begin{table}[]
    \centering
    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase, in suggested position within the pipeline. Augmentations that work well in more than one phase are listed in the last column.}
    \resizebox{0.9\textwidth}{!}{
    \begin{tabular}{llll}
    \toprule
        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} & \textbf{Multiple} \\
        \midrule
        \textsf{BleedThrough} &  \textsf{ColorPaper}& \textsf{BadPhotoCopy} & \textsf{BrightnessTexturize} \\
        \textsf{LowInkLines} & \textsf{Watermark} & \textsf{BindingsAndFasteners} & \textsf{DirtyDrum} \\
        \textsf{InkBleed} & \textsf{Gamma} & \textsf{BookBinding} & \textsf{DirtyRollers} \\
        \textsf{Letterpress} & \textsf{LightingGradient} & \textsf{Folding} & \textsf{Dithering} \\
        & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
        & & \textsf{Markup} & \textsf{NoiseTexturize}\\
        & & \textsf{Faxify} & \textsf{PencilScribbles}\\
        & & \textsf{PageBorder} & \\
        \bottomrule
    \end{tabular}}
    \label{tab:augmentations}
\end{table}
